---
title: "The parameters in CROBAS"
author: 'Xianglin Tian'
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Parameters_pCROB}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Rprebasso)
dim(pCROB)
colnames(pCROB)
```

| No. of the column |  Tree species                 |  Scientific names |
|:------------------|:------------------------------|:-------------------|
|1                  | Scots pine     | _Pinus sylvestris_|
|2                  | Norway spruce  | _Picea abies_|
|3                  | Silver birch   | _Betula pendula_|
|4                  | European beech | _Fagus sylvatica_|
|5                  | Maritime pine  | _Pinus pinaster_|
|6                  | Blue gum       | _Eucalyptus globulus_ |
|7                  | Black locust   | _Robinia pseudoacacia_ |
|8                  | Poplar         | _Populus_ spp. |
|9                  | Hybrid eucalyptus | _Eucalyptus grandis_ x _Eucalyptus urophylla_ |
|10                 | Norway spruce (in Germany) | _Picea abies_ |
|11                 | Holm oak | _Quercus ilex _ |

| No. of the row|  Parameter |  Meaning |
|:-----|:---|:-------------------|
|1|cR|	Light level at crown base that prompts full crown rise (to follow height growth)|
|2|rhow|	Wood density (kg C / m3)
|3|sla|	Specific leaf area (m2/kg C) (all-sided)
|4|k|	Homogeneous extinction coefficient (all-sided)
|5|vf|	Leaf longevity (yr)
|6|vr|	Fine root longevity (yr)
|7|c|	Growth respiration rate (kg C / kg C / yr)
|8|mf|	Maintenance respiration rate of foliage
|9|mr|	Maintenance respiration rate of fine roots
|10|mw|	Maintenance respiration rate of wood
|11|z|	Foliage allometry parameter
|12|beta0|	Ratio of coarse root biomass to above-ground sapwood biomass
|13|betab|	Ratio of mean branch pipe length to crown length
|14|betas|	Ratio of mean pipe length in stem above crown base to crown length
|15|rhof2|	Ratio of foliage mass to cross-sectional area at crown base, kg C/m2
|16|s1|	Parameter relating to reduction of photosynthesis with crown length
|17|kRein|	Stand density index (reference DBH = 25 cm)
|18|s0scale|	Adjusting photosynthesis rate of per weight of foliage biomass
|19|x| Parameter for relating branch length to crown length
|20|aETS|	Effect of the effective temperature sum on the longevity of foliage and fine roots.
|21|alfar1|	Ratio of fine roots to foliage mass for site type 1
|22|alfar2|	Ratio of fine roots to foliage mass for site type 2
|23|alfar3|	Ratio of fine roots to foliage mass for site type 3
|24|alfar4|	Ratio of fine roots to foliage mass for site type 4
|25|alfar5|	Ratio of fine roots to foliage mass for site type 5
|26|sarShp|	Shape surface area of the crown
|27|S_branchMod|	For branch litter model
|28|conifers=1 or decidous=2| Relate to the basal area limit for harvesting	
|29|p0_ref|	A reference rate of potential photosynthesis
|30|ETS_ref|	A reference of effective temperature sum
|31|thetaMax|	Old growth about diameter/heigh allocation, not used currently
|32|H0max	| Old growth about diameter/heigh allocation, not used currently
|33|gamma|	Old growth about diameter/heigh allocation, not used currently
|34|kH|   Old growth about diameter/heigh allocation, not used currently
|35|decayVp1| Calculate deadWood using Gompetz function
|36|decayVp2| Calculate deadWood using Gompetz function
|37|decayVp3| Calculate deadWood using Gompetz function
|38|ksi	| Relating sapwood area and crown length
|39|sla0	| The specific leaf area at age 0
|40|tsla	| The age at which SLA reaches the average of leave from age 0 and mature
|41|zb| Ratio between dead branches length and mean pipe length
|42|aHdom| Dominant height model (Intercept)
|43|bHdom| Dominant height model (Slop)
|44|decayVp4| Calculate deadWood using Gompetz function
|45|fAa|The inverse of extra allocation level for seedlings' roots at age 0. The value should be fAa=0.3 when it's working.No effects when fAa=1.|
|46|fAb|The reference height for extra allocation level decrease to the half of age 0.|
|47|fAc|The changing speed of the extra allocation level to roots from young age to old age.|